Ext. suppl.

### 2023-04-12 ext_method.RMD
updates

- Antiboy table?
- Power calculation + rational?

@@

@@

RNA normalization: 
 1. weight = mean(weight) 
 2. RNA = mean(RNA)
 3. weight.mc = weight/mean(weight)
 4. RNA.weight = RNA / weight
 - weight = biopsy weight

@@

rRNA normalization: 
 1. Lambda expression was first calculated and stored in the data.frame "nf"
 2. Calculation of target expression
 3. Joined the lambda and target expression data.frames
 4. nf.w = expr / weight
 5. nf.w = nf.w / max(nf.w)
 6. nf.expr = log(expr / nf.w), nf.w = scale(nf.w) ?
 - expr = target expression 
 - weight = biopsy weight

@@

Protein normalization:
 1. tpl = tp - bg
 2. tpl = tpl/max(tpl)
 3. signal = signal / max(signal)
 4. norm.sign = signal / tpl
 5. pool = mean(pool)
 6. norm.sign = norm.sign / pool
 - tpl = total protein per lane
 - tp = total protein (mean gray pixels in lanes)
 - bg = background (mean gray pixels between lanes)
 - signal = pixels per band

@@

>>>>

@@

## Total protein blots

### Blot/Gel 1 & 4

Gel 1 overview:

* Ladder loaded in well 1 and 25.
* Pools loaded in well 6, 12 and 20.
* Well 2-5 = sample 1.1-1.4 (participant 101).
* Well 7-10 = sample 2.1-2.4. (participant 102).
* Well 11 + 13-15 = sample 3.1-3.4 (participant 103).
* Well 16-19 = sample 5.1-5.4 (participant 105).
* Well 21-24 = sample 6.1-6.4 (participant 106).

![](figures/archive/total_protein_gel1.PNG)

Gel 4 overview:

* Ladder loaded in well 1 and 26.
* Pools loaded in well 2, 7, 15 and 21.
* Well 3-6 = sample 6.4-6.1 (participant 106).
* Well 8-11 = sample 5.4-5.1 (participant 105).
* Well 12-14 + 16 = sample 3.4-3.1 (participant 103).
* Well 17-20 = sample 2.4-2.1 (participant 102).
* Well 22-25 = sample 1.4-1.1 (participant 101).

![](figures/archive/total_protein_gel4.PNG)

Blot/Gel 2 & 5

Gel 2 overview

* Ladder loaded in well 1 and 26.
* Pools loaded in well 6, 11, 19 and 25.
* Well 2-5 = sample 7.1-7.4 (participant 107).
* Well 7-10 = sample 8.1-8.4 (participant 108).
* Well 12-15 = sample 9.1-9.4 (participant 109).
* Well 16-18 + 20 = sample 12.1-12.4 (participant 112).
* Well 21-24 = sample 13.1-13.4 (participant 113).

![](figures/archive/total_protein_gel2.PNG)

Gel 5 overview

* Ladder loaded in well 1 and 26.
* Pools loaded in well 2, 8, 16 and 21.
* Well 3-6 = sample 13.4-13.1 (participant 113).
* Well 7 + 9-11 = sample 12.4-12.1 (participant 112).
* Well 12-15 = sample 9.4-9.1 (participant 109).
* Well 17-20 = sample 8.4-8.1 (participant 108).
* Well 22-25 = sample 7.4-7.1 (participant 107).

![](figures/archive/total_protein_gel5.PNG)

Blot/Gel 3 & 6

Gel 3 overview

* Ladder loaded in well 1 and 17.
* Pools loaded in well 2, 7 and 13.
* Well 3-6 = sample 14.1-14.4 (participant 114).
* Well 8-11 = sample 15.1-15.4 (participant 115).
* Well 12 + 14-16 = sample 16.1-16.4 (participant 116).

![](figures/archive/total_protein_gel3.PNG)

Gel 6 overview

* Ladder loaded in well 1 and 17.
* Pools loaded in well 5, 11 and 16.
* Well 2-4 + 6 = sample 16.4-16.1 (participant 116).
* Well 7-10 = sample 15.4-15.1 (participant 115).
* Well 12-15 = sample 14.4-14.1 (participant 114).

![](figures/archive/total_protein_gel6.PNG)

@@

RNA normalization:

 1. weight = mean(weight) 
 2. RNA = mean(RNA)
 3. weight.mc = weight/mean(weight)
 4. RNA.weight = RNA / weight
    + weight = biopsy weight

@@

rRNA normalization:

 1. Lambda expression was first calculated and stored in the data.frame "nf"
 2. Calculation of target expression
 3. Joined the lambda and target expression data.frames
 4. nf.w = expr / weight
 5. nf.w = nf.w / max(nf.w)
 6. nf.expr = log(expr / nf.w), nf.w = scale(nf.w) ?
    + expr = target expression 
    + weight = biopsy weight

@@

Protein normalization:

 1. tpl = tp - bg
 2. tpl = tpl/max(tpl)
 3. signal = signal / max(signal)
 4. norm.sign = signal / tpl
 5. pool = mean(pool)
 6. norm.sign = norm.sign / pool
    + tpl = total protein per lane
    + tp = total protein (mean gray pixels in lanes)
    + bg = background (mean gray pixels between lanes)
    + signal = pixels per band

@@

### Statistical models

RNA

```{r total RNA model}
totalrna.model <- readRDS("./data/data-gen/rna/totalrna.model.RDS")

totalrna.model

```

Protein

```{r protein model}
protein.model <- readRDS("./data/data-gen/protein/protein.model.RDS")

protein.model

```

Protein/RNA correlation

```{r correlation model}
correlation.model <- readRDS("./data/data-gen/protein/correlation.model.RDS")

correlation.model

```

Strength, plasma glucose & c-peptide, nutrition and volume

```{r strength, plasma, nutrition and volume model}
strength.model <- readRDS("./data/data-gen/humac/strength.model.RDS")

strength.model

```
